# importing libraries
```{r message=FALSE, warning=FALSE}
library(readxl)
library(gt)
```


# select the data to be used for calculating SDS: trackman or synergy?
# best if imported via csv, if webscraping, update code here
```{r}
# going to write a function once I get trackman data that ensures seamless transition here
datasource = "synergy"

data <- read_excel("~/B1G Baseball Data 2019.xlsx")
```


# the following code allows for the execution of source code
# Models were built out in individual .Rmds and need to be executed for SDS calculation
# ensure that the notebooks are in the same project / file path
# individual model buildouts with visualizations can be consulted more closely in the 
# corresponding notebooks
```{r, message=FALSE, warning=FALSE}
source_rmd <- function(file, local = FALSE, ...){
  options(knitr.duplicate.label = 'allow')

  tempR <- tempfile(tmpdir = ".", fileext = ".R")
  on.exit(unlink(tempR))
  knitr::purl(file, output=tempR, quiet = TRUE)

  envir <- globalenv()
  source(tempR, local = envir, ...)
}

source_rmd("strikeprobability.Rmd")
source_rmd("swing_probability.Rmd")
source_rmd("contact_value.Rmd")
source_rmd("contact_probability.Rmd")
```

# creating a dataframe with every pitch for which we have pitch location data, and which
# includes our metrics to be utilized in SDS calculation
```{r}
source_rmd("compiler.Rmd")
```


```{r}
batters
```
```{r}
plot <- ggplot() + 
  geom_point(data=batters, aes(x=Season_SDS, y=OPS)) +
  geom_smooth(data=batters, aes(x=Season_SDS, y=OPS), method="lm")
```


```{r}
top_batters <- batters %>% head(n=10) %>% select(Batter, PA, Season_SDS)

top_batters %>% 
  gt() %>% 
  cols_label(Season_SDS = "Swing Decision Score", Batter = "Batter") %>%
  tab_header(
    title = "Top SDS Performers 2019",
    subtitle = "Sum of Swing Decision Score Over the 2019 Season"
  ) %>%
  tab_style(
    style = cell_text(color = "black", weight = "bold", align = "left"),
    locations = cells_title("title")
  ) %>% 
  tab_style(
    style = cell_text(color = "black", align = "left"),
    locations = cells_title("subtitle")
  ) %>%
  tab_style(
     locations = cells_column_labels(columns = everything()),
     style = list(
       cell_borders(sides = "bottom", weight = px(3)),
       cell_text(weight = "bold", size=12)
     )) %>%
tab_source_note(
    source_note = md("**By:** Collin Dougherty")
  ) %>% tab_options(row.striping.include_table_body = FALSE, table.background.color = "white") %>% 
  opt_row_striping(FALSE)
```